Accessing biological data with semantic web technologies

### 2013-12-31 article.tex
Added ToxBank and Open PHACTS grant details

The people who have provided feedback on the rrdf package are kindly thanked for their efforts in
getting into contact with me.

>>>>

The people who have provided feedback on the rrdf package are kindly thanked for their efforts in
getting into contact with me.
The research leading to these results has received funding from the European Community’s Seventh
Framework Programme (FP7/2007–2013) under Grant Agreement n° [267042], from Cosmetics Europe, 
and from the Innovative Medicines Initiative Joint Undertaking under grant agreement no. 115191,
resources of which are composed of financial contribution from the European Union's Seventh Framework
Programme (FP7/2007-2013) and EFPIA companies’ in-kind contribution.
